Enhancing Underwater Imagery using Generative Adversarial Networks

### 2017-10-25 files/paper/PlainPaper.tex
removed air force tag

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA,
  and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
 {\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
 %, fabbr013@umn.edu\}} \newline
 {\tt\small\{$^{1}$fabbr013,$^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}

>>>>

\title{Enhancing Underwater Imagery using Generative Adversarial Networks}
\author{Cameron Fabbri$^{1}$, Md Jahidul Islam$^{2}$, and Junaed Sattar$^{3}$
\thanks{				
  The authors are with the Department of Computer Science and Engineering, University of Minnesota-Twin  Cities, MN 55455, USA.
  %and the $^{1}$Air Force Research Laboratory, Rome, NY \newline
 %{\tt\small\{$^{1}$cameron.fabbri@us.af.mil\}} \newline
 %, fabbr013@umn.edu\}} \newline
 {\tt\small\{$^{1}$fabbr013,$^{2}$islam034, $^{3}$junaed\}@umn.edu}
}
}
